---
title: "工具變數"
output: html_notebook
---
# Download data and unzip the data
```{r}
rm(list=ls())
download.file('http://economics.mit.edu/files/397', 'asciiqob.zip')
unzip('asciiqob.zip')
```

# Read the data into a dataframe
qob:quarter of birth
yob:year of birth
pob: place of birth (state level)
```{r}
pums        <- read.table('asciiqob.txt',
                          header           = FALSE,
                          stringsAsFactors = FALSE)
names(pums) <- c('lwklywge', 'educ', 'yob', 'qob', 'pob')
```

# 計算不同出生年yob及出年季qob下的平均
dplyr::summarise_each()計算個別變數特徵值，並用原變數名稱命名。
```{r}
library(dplyr)
pums.qob.means  <- pums %>% group_by(yob, qob) %>% summarise_each(funs(mean))
```

# 產生日期變數
```{r}
library(lubridate)
yq.txt<-paste(paste("19",pums.qob.means$yob,sep=""),pums.qob.means$qob,sep="-")
pums.qob.means$yqob <- yq(yq.txt)
```

# 出生季節與教育年限
```{r}
library(ggplot2)
pums.qob.means %>% ggplot(aes(x = yqob, y = educ)) +
  geom_line() +
  geom_point(aes(color=qob)) 

pums.qob.means$qob2<-factor(pums.qob.means$qob)
pums.qob.means %>% ggplot(aes(x = yqob, y = educ)) +
  geom_line() +
  geom_point(aes(color=qob2))
```

# 出生季節與薪資
```{r}
pums.qob.means %>% ggplot(aes(x = yqob, y = lwklywge)) +
  geom_line() +
  geom_point(aes(color=qob2))
```

# 簡單OLS
```{r}
col1 <- lm(lwklywge ~ educ, pums)
```

# OLS 控制 YOB, POB
類別變數必需先使用factor()轉換
```{r}
col2 <- lm(lwklywge ~ educ + factor(yob) + factor(pob), pums)


```
OLS結果比較
```{r, warning=FALSE}
library(stargazer)
stargazer(col1,col2,type='text',keep='educ',
          column.labels = c('OLS','OLS.yob.pob'))
```

# 使用qob當工具變數
創造qob虛擬變數
```{r}
library(dummies)
qob.dummies<-dummy(pums$qob)
pums<-data.frame(pums,qob.dummies)
```

# IV: 2SLS with instrument QOB = 1
```{r}
library(AER)
# library(psych)
# describe(pums)
col3 <- ivreg(lwklywge ~ educ, ~ qob1, pums)
```

# IV: 2SLS with YOB, POB dummies and instrument QOB = 1
```{r}
col4 <- ivreg(lwklywge ~ factor(yob) + factor(pob) + educ,
	                   ~ factor(yob) + factor(pob) + qob1,
	          pums)
```


# Create dummy for quarter 1 or 2
```{r}
library(magrittr)
pums %<>% mutate(qob1or2=(qob == 1 | qob == 2))
```

# IV: 2SLS with YOB, POB dummies and instrument (QOB = 1 | QOB = 2)
```{r}
col5 <- ivreg(lwklywge ~ factor(yob) + factor(pob) + educ,
                       ~ factor(yob) + factor(pob) + qob1or2,
              pums)
```

# IV: 2SLS with YOB, POB dummies and full QOB dummies
```{r, warning=FALSE}
col6 <- ivreg(lwklywge ~ factor(yob) + factor(pob) + educ,
	                   ~ factor(yob) + factor(pob) + factor(qob),
	          pums)
```

# Column 7: 2SLS with YOB, POB dummies and full QOB dummies interacted with YOB
交叉作用符號*與:，詳見Introduction to R裡的11.1 Defining statistical models; formulae. 
```{r, warning=FALSE}
col7 <- ivreg(lwklywge ~ factor(yob) + factor(pob) + educ,
	                   ~ factor(pob) + factor(qob) * factor(yob),
	          pums)

```
# 綜合報表輸出
```{r, warning=FALSE}
stargazer(col2,col3,col4,col5,col6,col7,type="text",
          column.labels = c("yob.pob.OLS",
                            "IV.qob1","yob.pob.IV.qob1",
                            "yob.pob.IV.qob1or2",
                            "yob.pob.IV.qoball",
                            "yob.pob.IV.qob*yob"),
          keep="educ")
```

# 假設檢定
利用summary(.,diagnostic = TRUE)
```{r}
summary(col7,diagnostics = TRUE)
```

